Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-12-11 manuscript/paper-tycho.tex
Paper fixes; sent draft+diff around

\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
%\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
%\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
%\documentclass[iop, apj, numberedappendix]{emulateapj}

@@

% TODO define loss-limited properly...
% ~210 words -- a little too long
\begin{abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
scenarios, hence X-ray rim widths alone cannot discriminate between models.
Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
and particle diffusion coefficients $\abt1$--$100\times$ Bohm values,
consistent with prior work on Tycho's SNR, whereas magnetic damping permits
magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
coefficients (typically $\abt 1$--$10$).
Corresponding thin rim radio rims require magnetic damping, however.  We
jointly model radio and X-ray profiles and estimate magnetic damping length of
order $1$--$5$\% of remnant radius, with magnetic field strengths $\abt
50$--$400 \muG$ assuming Bohm diffusion.  Diffusion coefficients, magnetic
field strengths, and magnetic damping lengthscales are somewhat degenerate in
setting observed rim widths and drop-offs.
Although the energy dependence of synchrotron rims cannot discriminate magnetic
field structure, joint radio and X-ray modeling favors magnetic damping in
Tycho's SNR.
\end{abstract}

@@

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  The strong
and time-variable synchrotron radiation \citep[e.g.,][]{uchiyama2007,
patnaude2007}, in conjunction with multiwavelength spectral modeling
\citep{aharonian2004, acero2010, ackermann2013}, suggests that electrons are
accelerated to PeV energies in young SNRs.  Although synchrotron emission due
to accelerated electrons does not imply acceleration of an unseen hadronic
component, the prevailing theory of diffusive shock acceleration (DSA) should
operate on both positive ions and electrons.  Efficient hadron acceleration in
supernova remnant shocks is a prime candidate source for galactic cosmic rays
up to the cosmic ray spectrum's ``knee'' \citep{vink2012}.

@@

% Magnetic damping?
Magnetic damping immediately behind the shock offers an alternative explanation
for filament rims that requires less extreme magnetic field amplification, and
the possibility of damping in SNR shocks has not been fully tested
\citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} examined radio and
X-ray synchrotron rim profiles, but found that neither damping nor synchrotron
losses matched radio profiles particularly well.  \citet{araya2010} measured
rims at multiple energy bands in Cas A, but suggested that the rims only narrow
more weakly than expected and did not consider magnetic damping.
\citet{rettig2012} gave model predictions for several historical SNRs and
proposed discriminating based on filament spectra -- the expectation is that
damped spectra are softer, loss-limited harder.  Recently, \citet{ressler2014}
further extended the idea of discriminating between damped or loss-limited rims
by measuring rim width energy dependence in X-ray energies and found that rims
consistently narrowed in the remnant of SN 1006.

@@

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We selected and measured rim widths at several locations around Tycho's forward
shock, verifying that selected rims are free of thermal line emission.  Using a
model for particle transport with an exponentially cut-off injected electron
spectrum, we fit width measurements to model predictions in the loss-limited
and magnetic damping scenarios to obtain estimates on magnetic field strength
and diffusion coefficient magnitude.  We discuss degeneracy in our model fits
and the implications for future studies of young supernova remnant shocks.

@@

% Set choice of fiducial energy, eta_2
For subsequent analysis and model fitting, we take fiducial electron energy
$E_2 = E_h$ corresponding to a $2 \unit{keV}$ synchrotron photon and report all
model fit results in terms of $\eta_2 = \eta_h$.  Although the value of $E_2$
varies with magnetic field $B$ as $E_2 \propto B^{-1/2}$ and may vary within
the remnant, tying $\eta_h$ to a fixed observation energy gives a convenient
and intuitive sense of diffusion strength regardless of the underlying electron
energies.  We also note that $\eta = \eta_2 (E_2)^{1-\mu}$.

@@

The electron cut-off energy (equation~\eqref{eq:ecut}) depends on the magnetic
field, which varies in a damped model.  For simplicity, we assume that the
shock acceleration process is set by the diffusion at the immediate shock and
so equation~\eqref{eq:ecut} stands as evaluated with magnetic field strength
$B_0$.
\note[Aaron]{Is this correct?  Can rederive the expression (particles
penetrate some distance downstream, then back), but I'm not sure if it's even
sensible with diffusion coefficient varying so sharply.}

The solutions to equation~\eqref{eq:model} given by \citet{lerche1980,
rettig2012} assume $D(x) B^2(x)$ constant in order to make
equation~\eqref{eq:model} semi-analytically tractable.  Although unphysical, we
enforce this criterion by using a modified diffusion coefficient in our
calculations following
\citet{rettig2012}, given as:
\begin{equation} \label{eq:ddamp}
    D(E,x) = \frac{\eta C_d E^\mu}{B_0}
             \left[ \frac{\Bmin}{B_0} +
                    \frac{B_0 - \Bmin}{B_0} e^{-x/a_b} \right]^{-2}
\end{equation}
This strengthens the spatial-dependence of the diffusion coefficient, as
compared to the expected $D(x) \propto 1/B(x)$.
% TODO
%\note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
%will check shortly}

@@

We shall see below that this is qualitatively correct in setting model
predictions of rim shapes (within $\abt a_b$ of the shock front), but our
results are complicated by the increasing importance of energy-dependent
synchrotron losses downstream of the thin rim.  As we use FWHM as a singular
proxy for rim shapes, our procedure is not able to discern the transition in
shape downstream of the damped rim that may impact profile FWHMs, even as
damping controls the main observed rim emission.

@@

% NOTE keep region/filament numbering up to date
We selected 20 regions in 5 distinct filaments around Tycho's shock
(Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
clear of spatial plumes of thermal ejecta in \Chandra images, which rules out,
e.g., areas of strong thermal emission on Tycho's eastern limb; (2) filaments
should be singular and localized; multiple filaments should either not
overlap or completely overlap (rules out parts of NE limb); (3) filament
peaks should be evident above the background signal or downstream thermal
emission (rules out faint southern filaments).  We accepted several
regions with poor quality peaks in the lowest energy band ($0.7$--$1
\unit{keV}$) so long as peaks in all higher energy bands were clear and
well-fit.  We grouped regions into filaments by visual inspection of the
remnant.  Within each filament, we chose region widths to obtain comparable
counts at the thin rim peak.  All measured rim widths are at least $1\arcsec$
and hence are resolved by \textit{Chandra}'s point-spread function (PSF), which
has FWHM of $\abt 1\arcsec$ at $4\arcmin$ off-axis.

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.2\textwidth]{figures/snr.pdf}
    }{
        \plotone{figures/snr.pdf}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \label{fig:snr}}
\end{figure}
% NOTE keep region # bolding updated to match displayed filaments

@@

We extracted spectra at and immediately behind thin rims in each region
(``'rim'', ``downstream'' spectra respectively) to confirm that rim width
measurements are not affected by contaminating thermal line emissions.  We
used our empirical fits of rim profile shape (Section~\ref{sec:fwhms} below)
to select two corresponding sections in each region for spectrum extraction.
The rim section is the smallest sub-region containing the measured FWHM bounds
from all energy bands.  The downstream section extends from the rim section's
downstream edge to the farthest downstream profile fit domain bound, in all
energy bands (fits of equation~\eqref{eq:prof}); i.e., the downstream section
is bounded by the thin rim FWHM and the intensity plateau/trough behind the
rim.  To illustrate our selections, Figure~\ref{fig:spec} plots example rim
profiles ($4.5$--$7 \unit{keV}$) with the downstream and rim sections
highlighted.

% Spectrum data, binning, background
Spectra taken from all enumerated \Chandra ObsIDs (Section~\ref{sec:regions})
were grouped into bins of $\geq 15$ counts.  We extracted background spectra
from circular regions (radius $\abt 30\arcsec$) around the remnant's exterior;
each region's rim and downstream spectra subtracted the closest background
region's spectrum.
% Background region size is valid for data-tycho/bkg-2/ selections

@@

% How we ran model fits (itemize knobs, explain energy band mapping, errors,
% fitting procedure
We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
measured rim widths as a function of energy by varying several physical
parameters: magnetic field strength $B_0$, normalized diffusion coefficient
$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
$\Bmin$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
mapped each width measurement to the lower energy limit of its energy band;
e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
profile widths at $0.7 \unit{keV}$.  Width errors in our least squares fits
average the positive and negative errors on each FWHM measurement.  For an
input set of model parameters, we numerically computed intensity profiles and
hence model FWHMs as detailed in Section~\ref{sec:transport}, and used a
Levenberg-Marquardt fitting routine to identify best fit model parameters.
To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
initial guesses for fitting.
% TODO this may be obsoleted if we recompute stuff...  I only computed errors
% on the loss-limited model, and those fits are now out of date too...
%Errors on best fit parameters were computed by varying each fit parameter and
%obtaining a new best fit model, with one less degree of freedom, to find the
%parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.

@@

% Observations of mE and rim widths, errors
Although the measurement scatter is quite large, shown dramatically in the
point-wise computed $\mE$ values, the mean rim width decreases consistently
with increasing energy.  Furthermore, mean $\mE$ values are consistently
negative and tend smoothly towards $0$ (weaker energy-dependence) with
increasing energy.  The errors on FWHM measurements are typically $\abt 10\%$
or smaller, reflecting the high quality \Chandra data as also seen in
Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
part to (1) our profile fitting procedure, which depends on a somewhat
arbitrary choice of profile fit function, and (2) variation in Tycho's rim
morphology (e.g., Figure~\ref{fig:profiles}).

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \epsscale{0.5}
    }{}
    \plotone{figures/prfs-fit-01.pdf} \\
    \plotone{figures/prfs-fit-16.pdf}
    \caption{Best fit full model rim profile width predictions for Regions 1
        (top) and 16 (bottom) for loss-limited and damped scenarios with
        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Model
        parameters are given in Table~\ref{tab:fits-all}.  Shaded regions on
        damped profiles indicate the magnetic field damping lengthscale $a_b$.
        \label{fig:rims}}
\end{figure}

@@

Here we first explore trends in our data and best-fit diffusion and magnetic
fields.  We then discuss discrimination of the loss-limited and damping models
(i.e., our ability to favor or constrain a finite value of $a_b$), and possible
paths forward to better constrain our model parameters.

@@

% First address the broad trend of leveling energy dependence in mE)
We suggest that the observed decrease in $|\mE|$ with increasing energy
(Table~\ref{tab:fwhms}) is caused by diffusion, which weakens width-energy
dependence at higher energies.  The photon energy at which $l_{\mt{ad}} =
l_{\mt{diff}}$ is exactly the synchrotron cut-off energy,
% TODO citation if you can find it...
$\abt 0.3 \unit{keV}$ in Tycho \citep{hwang2002}.  Diffusion should begin
overtaking advection and push $\mE$ towards $0$ in soft X-rays, as opposed to
$\mE \abt -0.5$ expected for strong advection (Section~\ref{sec:energydep}).  A
decrease in $|\mE|$ is then reassuringly consistent with the framework of
diffusive shock acceleration.

% Discuss variability in width measurements
The large scatter in filament widths and hence scatter in point-wise computed
$\mE$ values (Table~\ref{tab:fwhms}) relegates our interpretation of $\mE$ to
conjecture.  Filament widths both increase and decrease between energy bands in
multiple regions, and diffusion ($\eta_2$) and hence $\Ecut$ are poorly
constrained by our fit results.  Our averaged results should mitigate the
effects of measurement scatter, however.

@@

% lad/ldiff scalings give eta/B0 scalings
In the loss-limited model, we find roughly that $\eta_2 \propto d^2$ while
$B_0$ is approximately constant.  The advective lengthscale,
equation~\eqref{eq:lad}, may be rearranged to obtain:
\begin{align}
    B_0 =\; &(317 \muG) \left(\frac{v_d}{10^8 \unit{cm/s}}\right)^{2/3}
                \nonumber \\
            &\times \left(\frac{l_{\mt{ad}}}{0.01 \unit{kpc}}\right)^{-2/3}
                \left(\frac{h\nu}{1 \unit{keV}}\right)^{-1/3}
\end{align}
% TODO if we keep this equation, double check the 317 \muG carefully...
or, more simply,
\begin{equation}
    B_0 \propto \left(v_d\right)^{2/3}
                \left(l_{\mt{ad}}\right)^{-2/3} \nu^{-1/3} .
\end{equation}
Both $l_{\mt{ad}}$ and $v_d$ scale linearly with remnant distance $d$ and thus
their effects cancel in determining the magnetic field.  If diffusion is the
primary control on filament lengthscales, equation~\eqref{eq:ldiff} yields:
\begin{equation}
    \eta \propto \left(l_{\mt{diff}}\right)^2 B_0^{3} \nu^{-(\mu - 1)/2}
\end{equation}
Recall that $\eta \propto \eta_2$ since $E_h = E_2$ is constant for a given
$B_0$, from equation~\eqref{eq:diffcoeff}.  Similar results, primarily for
magnetic field $B_0$, were previously given by \citet{parizot2006}.

@@

To measure synchrotron cut-offs in Tycho, we fitted rim spectra
(Section~\ref{sec:spec}) to the XSPEC model \texttt{srcut}, modified to fit in
log-frequency units.  Column density $N_{\mt{H}}$ and cut-off frequency
$nu_{\mt{cut}}$ are free parameters; we fixed the radio spectral index $\alpha
= 0.58$ as done in our profile modeling \citep{sun2011}.
Table~\ref{tab:fits-srcutlog} presents the spectrum fit parameters and best
loss-limited fits with $\nu_{\mt{cut}}$-derived $\eta_2$ fixed.
Variation in $\mu$ has a small effect on best fits; Regions 1 and 16 have best
fit values of $B_0$ increasing over $252$--$266 \muG$ and $660$--$700 \muG$
respectively as $\mu$ ranges between $0$--$2$.

The results are comparable to fits with $\eta_2 = 1$ fixed
(Table~\ref{tab:fits-all-eta2one}).  The synchrotron cut-off frequency is
typically $0.3 \unit{keV}$, though we note that Regions 11, 12 have unusually
high cut-off frequencies.  Fitted $B_0$ values span $250$--$700 \muG$.
We cannot deduce any particular insight from requiring that $\eta_2$ reflects
the measured value of $\nu_{\mt{cut}}$.  But, if the diffusion coefficients are
more reliable or physically reasonable, the derived estimates of $B_0$ may be
more credible.

>>>>

\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
%\documentclass[iop, apj, numberedappendix]{emulateapj}

%\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
%\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}

@@

% TODO define loss-limited properly...
% ~210 words -- a little too long
\begin{abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
scenarios, hence X-ray rim widths alone cannot discriminate between models.
Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
and particle diffusion coefficients $\abt1$--$100\times$ Bohm values, whereas
magnetic damping permits magnetic fields of $\abt 10$--$300 \muG$ and
comparatively smaller diffusion coefficients (typically $\abt 1$--$10$).
Corresponding thin rim radio rims require magnetic damping, however.  We
jointly model radio and X-ray profiles and estimate magnetic damping length of
order $1$--$5$\% of remnant radius, with magnetic field strengths $\abt
50$--$400 \muG$ assuming Bohm diffusion.  Diffusion coefficients, magnetic
field strengths, and magnetic damping lengthscales are somewhat degenerate in
setting observed rim widths and drop-offs.
Although the energy dependence of synchrotron rims cannot discriminate magnetic
field structure, joint radio and X-ray modeling favors magnetic damping in
Tycho's SNR.
\end{abstract}

@@

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  Strong and
time-variable synchrotron radiation \citep[e.g.,][]{uchiyama2007,
patnaude2007}, in conjunction with multiwavelength spectral modeling
\citep{aharonian2004, acero2010, ackermann2013}, suggests that electrons are
accelerated to PeV energies in young SNRs.  Although synchrotron emission due
to accelerated electrons does not imply acceleration of an unseen hadronic
component, the prevailing theory of diffusive shock acceleration (DSA) should
operate on both positive ions and electrons.  Efficient hadron acceleration in
supernova remnant shocks is a prime candidate source for galactic cosmic rays
up to the cosmic ray spectrum's ``knee'' \citep{vink2012}.

@@

% Magnetic damping?
Magnetic damping immediately behind the shock offers an alternative explanation
for filament rims that requires less extreme magnetic field amplification, and
the possibility of damping in SNR shocks has not been fully tested
\citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} modeled radio and
X-ray synchrotron rim profiles but could not simultaneously reproduce the
intensities of observed X-ray and radio rims with damped or loss-limited
magnetic fields.  \citet{araya2010} measured rims at multiple energy bands in
Cas A, but suggested that the rims only narrow more weakly than expected and
did not consider magnetic damping.  \citet{rettig2012} gave model predictions
for several historical SNRs and proposed discriminating based on filament
spectra -- the expectation is that damped spectra are softer, loss-limited
harder.  Recently, \citet{ressler2014} further extended the idea of
discriminating between damped or loss-limited rims by measuring rim width
energy dependence in X-ray energies and found that rims consistently narrowed
in the remnant of SN 1006.

@@

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We selected and measured rim widths at several locations around Tycho's forward
shock, verifying that selected rims are free of thermal line emission.  Using a
model for particle transport with an exponentially cut-off injected electron
spectrum, we fit width measurements to model predictions in the loss-limited
and magnetic damping scenarios to obtain estimates on magnetic field strength
and diffusion coefficient magnitude.  We discuss degeneracy in our model fits
and attempt to constrain damping through spectral variation downstream of the
forward shock and considering both radio and X-ray rim morphology.
%and the implications for future studies of young supernova remnant shocks.

@@

% Set choice of fiducial energy, eta_2
For subsequent analysis and model fitting, we take fiducial electron energy
$E_2 = E_h$ corresponding to a $2 \unit{keV}$ synchrotron photon and report all
model fit results in terms of $\eta_2 = \eta_h$.  Although the value of $E_2$
varies with magnetic field $B$ as $E_2 \propto B^{-1/2}$ and may vary within
the remnant, tying $\eta_h$ to a fixed observation energy gives a convenient
and intuitive sense of diffusion strength regardless of the underlying electron
energies.

@@

The electron cut-off energy (equation~\eqref{eq:ecut}) depends on the magnetic
field, which varies in a damped model.  For simplicity, we assume that shock
acceleration is controlled by diffusion at the immediate shock and so
equation~\eqref{eq:ecut} stands as evaluated with magnetic field strength
$B_0$.

The solutions to equation~\eqref{eq:model} given by \citet{lerche1980} assume
$D(x) B^2(x)$ constant to render equation~\eqref{eq:model} semi-analytically
tractable.  Although unphysical, we enforce this assumption by modifying the
diffusion coefficient as, following \citet{rettig2012}:
\begin{equation} \label{eq:ddamp}
    D(E,x) = \frac{\eta C_d E^\mu}{B_0}
             \left[ \frac{\Bmin}{B_0} +
                    \frac{B_0 - \Bmin}{B_0} e^{-x/a_b} \right]^{-2} .
\end{equation}
This strengthens the spatial-dependence of the diffusion coefficient, as
compared to the expected $D(x) \propto 1/B(x)$.
% TODO
%\note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
%will check shortly}

@@

We shall see below that this is qualitatively correct in setting model
predictions of rim shapes (within $\abt a_b$ of the shock front), but our
results are complicated by energy-dependent synchrotron losses downstream of
the thin rim.

@@

% NOTE keep region/filament numbering up to date
We selected 20 regions in 5 filaments around Tycho's shock
(Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
clear of spatial plumes of thermal ejecta in \Chandra images, which rules out,
e.g., areas of strong thermal emission on Tycho's eastern limb; (2) filaments
should be singular and localized; multiple filaments should either not
overlap or completely overlap (rules out parts of NE limb); (3) filament
peaks should be evident above the background signal or downstream thermal
emission (rules out faint southern filaments).  We accepted several
regions with poor quality peaks in the lowest energy band ($0.7$--$1
\unit{keV}$) so long as peaks in all higher energy bands were clear and
well-fit.  We grouped regions into filaments by visual inspection of the
remnant.  Within each filament, we chose region widths to obtain comparable
counts at the thin rim peak.  All measured rim widths are at least $1\arcsec$
and hence are resolved by \textit{Chandra}'s point-spread function (PSF), which
has FWHM $\lesssim 1\arcsec$ within $4\arcmin$ of the optical axis.

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        %\includegraphics[width=0.3\textwidth]{figures/snr.pdf}
        \includegraphics[width=0.3\textwidth]{figures/snr-inv.png}
    }{
        %\plotone{figures/snr.pdf}
        \plotone{figures/snr-inv.png}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \label{fig:snr}}
\end{figure}
% NOTE keep region # bolding updated to match displayed filaments

@@

We extracted spectra at and immediately behind thin rims in each region
(``rim'', ``downstream'' spectra respectively) to confirm that rim width
measurements are not contaminated by thermal line emission.  The two extraction
regions are determined by our empirical fits of rim profile shape
(Section~\ref{sec:fwhms}).  The rim section is the smallest sub-region
containing the measured FWHM bounds from all energy bands.  The downstream
section extends from the rim section's downstream edge to the farthest
downstream profile fit domain bound, in all energy bands (fits of
equation~\eqref{eq:prof}); i.e., the downstream section is bounded by the thin
rim FWHM and the intensity plateau/trough behind the rim.  To illustrate our
selections, Figure~\ref{fig:spec} plots example rim profiles ($4.5$--$7
\unit{keV}$) with the downstream and rim sections highlighted.

% Spectrum data, binning, background
Spectra were binned such that each datum had $\geq 15$ counts.  We extracted
background spectra from circular regions (radius $\abt 30\arcsec$) around the
remnant's exterior; each region's rim and downstream spectra subtracted the
closest background region's spectrum.
% Background region size is valid for data-tycho/bkg-2/ selections

@@

% How we ran model fits (itemize knobs, explain energy band mapping, errors,
% fitting procedure
We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
measured rim widths as a function of energy by varying several physical
parameters: magnetic field strength $B_0$, normalized diffusion coefficient
$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
$\Bmin$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
mapped each width measurement to the lower energy limit of its energy band;
e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
profile widths at $0.7 \unit{keV}$.  Width errors in our least squares fits
average the positive and negative errors on each FWHM measurement.  For a given
set of model parameters, we numerically computed intensity profiles and
hence model FWHMs as detailed in Section~\ref{sec:transport}; we then used a
Levenberg-Marquardt fitter to seek model parameters yielding best fit FWHMs.
To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid
parameters as initial guesses for fitting.
% TODO this may be obsoleted if we recompute stuff...  I only computed errors
% on the loss-limited model, and those fits are now out of date too...
%Errors on best fit parameters were computed by varying each fit parameter and
%obtaining a new best fit model, with one less degree of freedom, to find the
%parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.

@@

% Observations of mE and rim widths, errors
Although the measurement scatter is quite large, shown dramatically in the
point-wise computed $\mE$ values, the mean rim width decreases consistently
with increasing energy.  Furthermore, mean $\mE$ values are consistently
negative and tend smoothly towards $0$ (weaker energy-dependence) with
increasing energy.  Errors on FWHM measurements are typically $\lesssim 10\%$,
reflecting the high quality of the underlying \Chandra data.  Scatter in FWHM
measurements may be attributed in part to (1) our profile fitting procedure,
which depends on a somewhat arbitrary choice of profile fit function, and (2)
variation in Tycho's rim morphology (e.g., Figure~\ref{fig:profiles}).

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \epsscale{0.7}
        \plotone{figures/prfs-fit-01.pdf} \\
        \plotone{figures/prfs-fit-16.pdf}
        \epsscale{1}
    }{
        \plotone{figures/prfs-fit-01.pdf} \\
        \plotone{figures/prfs-fit-16.pdf}
    }
    \caption{Best fit full model rim profile width predictions for Regions 1
        (top) and 16 (bottom) for loss-limited and damped scenarios with
        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Model
        parameters are given in Table~\ref{tab:fits-all}.  Shaded regions on
        damped profiles indicate the magnetic field damping lengthscale $a_b$.
        \label{fig:rims}}
\end{figure}

@@

@@

% First address the broad trend of leveling energy dependence in mE)
We suggest that the observed decrease in $|\mE|$ with increasing energy
(Table~\ref{tab:fwhms}) is caused by diffusion, which weakens width-energy
dependence at higher energies.  The photon energy at which $l_{\mt{ad}} =
l_{\mt{diff}}$ is exactly the DSA-predicted synchrotron cut-off energy.
% TODO citation if you can find it...
Diffusion should begin overtaking advection and push $\mE$ towards $0$ in soft
X-rays, as opposed to $\mE \abt -0.5$ expected for strong advection
(Section~\ref{sec:energydep}).  A decrease in $|\mE|$ is then reassuringly
consistent with the framework of diffusive shock acceleration.

% Discuss variability in width measurements
The large scatter in filament widths and hence scatter in point-wise computed
$\mE$ values (Table~\ref{tab:fwhms}) relegates our interpretation of $\mE$ to
conjecture.  Filament widths both increase and decrease between energy bands in
multiple regions, and diffusion $\eta_2$ and hence $\Ecut$ are poorly
constrained by our fit results.  Our averaged results should mitigate the
effects of measurement scatter, however.

@@

% lad/ldiff scalings give eta/B0 scalings
In the loss-limited model, we find roughly that $\eta_2 \propto d^2$ with
$B_0$ approximately constant.  The advective lengthscale,
equation~\eqref{eq:lad}, may be rearranged to obtain:
\begin{align}
    B_0 =\; &(317 \muG) \left(\frac{v_d}{10^8 \unit{cm/s}}\right)^{2/3}
                \nonumber \\
            &\times \left(\frac{l_{\mt{ad}}}{0.01 \unit{kpc}}\right)^{-2/3}
                \left(\frac{h\nu}{1 \unit{keV}}\right)^{-1/3}
\end{align}
% TODO if we keep this equation, double check the 317 \muG carefully...
or, more simply,
\begin{equation}
    B_0 \propto \left(v_d\right)^{2/3}
                \left(l_{\mt{ad}}\right)^{-2/3} \nu^{-1/3} .
\end{equation}
Both $l_{\mt{ad}}$ and $v_d$ scale linearly with remnant distance $d$ and thus
their effects cancel in determining the magnetic field.  If diffusion is the
primary control on filament lengthscales, equation~\eqref{eq:ldiff} yields:
\begin{equation}
    \eta \propto \left(l_{\mt{diff}}\right)^2 B_0^{3} \nu^{-(\mu - 1)/2}
\end{equation}
Recall that $\eta \propto \eta_2$ since $E_h = E_2$ is constant for a given
$B_0$, from equation~\eqref{eq:diffcoeff}.  Similar results, primarily for
magnetic field $B_0$, were previously given by \citet{parizot2006}.

@@

To measure synchrotron cut-offs in Tycho, we fitted ``rim'' spectra
(Section~\ref{sec:spec}) to the XSPEC model \texttt{srcut}, modified to fit in
log-frequency units; we fix the radio spectral index $\alpha = 0.58$
\citep{sun2011} as done in our profile modeling and fit for column density
$N_{\mt{H}}$ and cut-off frequency $\nu_{\mt{cut}}$ in each region.  The
fitted cut-off frequency is typically $0.3 \unit{keV/h}$, consistent with fits
by \citet{hwang2002}, but Regions 11, 12 have unusually high cut-off
frequencies $0.55$, $0.88 \unit{keV/h}$ consistent with harder rim spectra
(Table~\ref{tab:spec}).

Using the derived values of $\nu_{\mt{cut}}$ ($0.19$--$0.88 \unit{keV/h}$) and
hence $\eta_2$ ($4$--$15$), we computed new loss-limited fits for all regions
with cut-off derived values of $\eta_2$ fixed.  Fitted $B_0$ values span
$250$--$700 \muG$.  Variation in $\mu$ has a smaller effect on best fits as we
are able to derive different $\eta_2$ values as a function of $\mu$; Regions 1
and 16 have best fit values of $B_0$ increasing over $252$--$266 \muG$ and
$660$--$700 \muG$ respectively as $\mu$ ranges between $0$--$2$.  Our fits with
cut-off derived values of $\eta_2$ are comparable to fits with $\eta_2 = 1$
fixed (Table~\ref{tab:fits-all-eta2one}).  We are unable to deduce any insights
from requiring that $\eta_2$ reflects measurements of $\nu_{\mt{cut}}$.  But,
diffusion coefficients computed in this manner may give more credible derived
estimates of $B_0$ if the DSA assumptions invoked are relevant.
